% LaTeX resume using res.cls
% Note: convert through ps to pdf for best results
%   ps2pdf resume.ps resume.pdf
\documentclass[margin]{res}


\usepackage[T1]{fontenc}
\usepackage{tipa}
%\usepackage{fullpage}
\usepackage{hyperref}

\usepackage{ifpdf}

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Evan H. Carmi}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:

\moveleft.5\hoffset\centerline{{\bf Phone: (541) 729-0334 $\parallel$ E-mail: evan@evancarmi.com $\parallel$ Web: https://evancarmi.com/}}
\address{{\bf Location:} Portland, OR}

\begin{resume}
\section{\textsc{Summary}} I combine deep technical expertise with high-level problem solving to find solutions to business problems.

\section{\textsc{Education}} {\bf Wesleyan University}, Middletown, CT \\ {\sl Bachelor of Arts} in Computer Science \\
    % \sl will be bold italic in New Century Schoolbook (or
    % any postscript font) and just slanted in
    % Computer Modern (default) font
    {\sl Cumulative G.P.A:} 3.94\\
    {\sl Awards:} Michael Rice Prize for Excellence in Computer Science, Dean's list
 
 
\section{\textsc{Technical \\ Skills}}
    Ruby, Rails, HTML/CSS, JavaScript, Amazon Web Services, Devops, Security, UX/UI \\

\section{\textsc{Experience}}
    {\sl Senior Software Engineer} \hfill 2015 - Present \\ Cambia Health Solutions
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Played a leadership role in the development, infrastructure and security of a new internal business from prototype to public launch.
    \end{itemize}

    {\sl Founder and Principal Engineer} \hfill 2015 - Present \\ CarmiMedia, LLC
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Founded and led a consultancy bridging technology and business. Worked with local companies and startups to design and build software that delivers business goals: https://evancarmi.com
    \end{itemize}

    {\sl Software Engineer} \hfill 2013 - 2014 \\ Brewster
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item As an early developer of a VC-funded startup (acquired 2015), I held key technical roles including hiring, workflow management, architecture and feature implementation.
    \end{itemize}

    {\sl Consultant} \hfill 2008 - 2014
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Hired as consultant on numerous projects from developing web applications for university researchers to building a programmatic music synthesizer for a startup.
    \end{itemize}

    {\sl Software Engineer} \hfill Summer 2011 and Summer 2012 \\
    The New York Times
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Worked with Interactive News Technologies - a small, agile team of developers to design, build and run the New York Times' award-winning London 2012 Olympics website.
    \end{itemize}

    {\sl Programming Manager} \hfill 2009 - 2013 \\
    Instructional Media Services, Wesleyan University
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Managed and hired a team of student programmers implementing applications to monitor and control multimedia classrooms. Participated in the development of a touch-screen controlled audio-visual control system written in Ruby.
    \end{itemize}

\section{\textsc{Languages}} Fluent in English, French and Spanish.

\end{resume}
\end{document}
